Appendix: Stop Lying to Me: New Visual Tools to Choose the Most Honest Nonlinear Dimension Reduction

### 2025-06-26 appendix.qmd
Updated appendix with new notations

assign_data_vis1 <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
  geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
  geom_point(data = emb_df1, aes(x = emb1, y = emb2), color = "black", size = 0.7) +
  geom_text(data = all_centroids_df, aes(x = c_x, y = c_y, label = hexID), size = 5, colour = "#bdbdbd") +
  geom_circle(data = circles, aes(x0 = x, y0 = y, r = r), fill = NA) +
  geom_segment(x = 0.45, y = 0.47, xend = 0.58, yend = 0.3, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#969696") +
  geom_segment(x = 0.54, y = 0.56, xend = 0.4, yend = 0.715, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#969696")
```

@@

assign_data_vis2 <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
  geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
  geom_point(data = points_df, aes(x = x, y = y), color = "black", size = 0.7) +
  geom_text(data = all_centroids_df, aes(x = c_x, y = c_y, label = hexID), size = 5, colour = "#bdbdbd") +
  geom_segment(data = arrow_df, aes(x = x, y = y, xend = xend, yend = yend), 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") 
```

@@

error_pbmc <- error_pbmc |>
  mutate(a1 = round(a1, 2)) |>
  filter(bin1 >= 5) |>
  group_by(method, a1) |>
  filter(RMSE == min(RMSE)) |>
  ungroup()
```

>>>>

assign_data_vis1 <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
  geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
  geom_point(data = emb_df1, aes(x = emb1, y = emb2), color = "black", size = 0.7) +
  geom_text(data = all_centroids_df, aes(x = c_x, y = c_y, label = h), size = 5, colour = "#bdbdbd") +
  geom_circle(data = circles, aes(x0 = x, y0 = y, r = r), fill = NA) +
  geom_segment(x = 0.45, y = 0.47, xend = 0.58, yend = 0.3, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#969696") +
  geom_segment(x = 0.54, y = 0.56, xend = 0.4, yend = 0.715, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#969696")
```

@@

assign_data_vis2 <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
  geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
  geom_point(data = points_df, aes(x = x, y = y), color = "black", size = 0.7) +
  geom_text(data = all_centroids_df, aes(x = c_x, y = c_y, label = h), size = 5, colour = "#bdbdbd") +
  geom_segment(data = arrow_df, aes(x = x, y = y, xend = xend, yend = yend), 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") 
```

@@

error_pbmc <- error_pbmc |>
  mutate(a1 = round(a1, 2)) |>
  filter(b1 >= 5) |>
  group_by(method, a1) |>
  filter(RMSE == min(RMSE)) |>
  ungroup()
```
